### 2016-02-01 math_modeling/class/notes/classnotes.tex
working hard or something

\subsection{Modeling War}
We will model the Nazi party and the Soviet Union military forces. We want to model the rate
at which Soviet Tanks reduce as Nazi anti-tank guns decrease.
\begin{gather*}
\frac{dx}{dt} = -ay\\
\frac{dy}{dt} = -bx
\end{gather*}
In this system, $x'$ represents the rate at which the Soviet tanks decreased, and $y'$ represents
the rate at which German anti-tank guns decrease. We will consider the battle of Kursk, during
which the number of Soviet tanks decreased by $50\%$ in the first hour. In this model, $a$ is
referred to as the anti-tank kill rate, where $b$ is the tank kill rate. We can use separation
of variables yields
\begin{gather*}
{ay^2\over2}+{ay_{0}^{2}\over2} = {bx^2\over2}+{bx_{0}^{2}\over2}\\
ay^{2}-bx^{2}=C
\end{gather*}
\end{document}

>>>>

\subsection{Modeling War}
We will model the Nazi party and the Soviet Union military forces. We want to model the rate
at which Soviet Tanks reduce as Nazi anti-tank guns decrease.
\begin{gather*}
\frac{dx}{dt} = -ay\\
\frac{dy}{dt} = -bx
\end{gather*}
In this system, $x'$ represents the rate at which the Soviet tanks decreased, and $y'$ represents
the rate at which German anti-tank guns decrease. We will consider the battle of Kursk, during
which the number of Soviet tanks decreased by $50\%$ in the first hour. In this model, $a$ is
referred to as the anti-tank kill rate, where $b$ is the tank kill rate. We can use separation
of variables yields
\begin{gather*}
{ay^2\over2}+{ay_{0}^{2}\over2} = {bx^2\over2}+{bx_{0}^{2}\over2}\\
ay^{2}-bx^{2}=C
\end{gather*}

\section{Agents}
A Schelling Model is used to model things like segregation. Consider the following example:
\begin{center}
\begin{tabular}{c c c c c c}
x1 & x2 &    &    &    &    \\
x3 & o1 &    & o2 &    &    \\
x4 & x5 & o3 & o4 & o5 &    \\
x6 & o6 &    &    & x7 & x8 \\
   & o7 & o8 & x9 & x10 & x11 \\
   &    & o9 & o10 & o11 & \\
\end{tabular}
\end{center}
We can consider the case where, in the first iteration, all the members of the grid who do not have
three directly adjacent neighbors leave the area. In addition, x's want to be with other x's, and
o's want to be with other o's.
\begin{center}
\begin{tabular}{c c c c c c}
   &    &    &    &    &    \\
x3 & x6 &    & o1 & o2 &    \\
x4 & x5 & o3 & o4 &    &    \\
   & o6 & x2 & x1 & x7 & x8 \\
o11& o7 & o8 & x9 & x10 & x11 \\
   &    & o5 & o9 & o10 & \\
\end{tabular}
\end{center}
We can see that as the system changes, there will be a mass exodus of both types. In the first table,
there was only 1 agent with no neighbors of the opposite type. By the second iteration, there are now 6
agents with no neighbors of the opposite type.
\end{document}

### 2016-02-01 number_theory/hw/hw3.tex
working hard or something

\begin{enumerate}
\item 
\end{enumerate}
\end{document}

>>>>

\begin{enumerate}
\item Suppose that $a,b\in\ZZ$ and define the set $J={ax+by|x,y\in\ZZ}$. Prove that $J=Z$ if and only if
$gcd(a, b) = 1$.

\item We define the \textit{Fibonacci Sequence} to be the sequence of integers ${x_{0}, x_{1}, x_{2},\dots}$
satisfying the properties
\[
x_{0} = 0,\quad x_{1} = 1,\quad\text{and}\quad x_{n} = x_{n-1}+x_{n}\text{ for all } n\geq2.
\]
Prove that $gcd(x_{n},x_{n-1}) = 1$ for all $n \geq 1$. (Hint: Try using induction on $n$.)

\item Let $a, b, x$ be positive integers with $x \geq 2$ and set $d = gcd(a, b)$.
\begin{enumerate}
\item Prove that $x^{d} - 1$ divides $gcd(x^{a} - 1, x^{b} - 1)$.

\item Prove that $x^{d}-1$ is a multiple of $gcd(x^{a}-1,x^{b}-1)$ and conclude that
$x^{d}-1 = gcd(x^{a}-1,x^{b}-1)$. (Hint: We know that there exist integers $u$ and $v$ such that
$d = au + bv$. Now show that there exist integers $\alpha$ and $\beta$ such that
$x^{d}-1 = \alpha(x^{a}-1) + \beta(x^{b}-1)$.)

\end{enumerate}

\item Show that the equation $1495x + 50060y = 4$ has no solutions for $x,y\in\ZZ$.
\begin{quote}
\begin{align*}
50060 &= 1495(33) + 725\\
1495 &= 725(2) + 45\\
725 &= 45(16) + 5\\
45 &= 5(9) + 0\\
gcd(50060,1495) &= 5
\end{align*}
However, $5\cancel{|}4$, so there is no solution.
\end{quote}

\item Find all solutions to the equation $1485x + 1745y = 15$ for $x,y\in\ZZ$.

\begin{center}
\begin{minipage}[t]{0.4\textwidth}
\begin{align*}
1745 &= 1485(1) + 260\\
1485 &= 260(5) + 185\\
260 &= 185(1) + 75\\
185 &= 72(2) + 35\\
75 &= 35(2) + 5\\
35 &= 7(5) + 0\\
gcd&(1745,1485) = 5
\end{align*}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{align*}
5 &= 75 - 35(2)\\
5 &= 75 - (185 - 75(2))(2)\\
&= 75(5) - 185(2)\\
5 &= (260-185(1))(5)-185(2)\\
&= 260(5)-187(7)\\
5 &= 260(5) - (1485 -260(5))(7)\\
&= 260(40) + 1485(-7)\\
5 &= (1745 - 1485(1))(40) + 1485(-7)\\
&= 1745(40) + 1485(-47)
\end{align*}
\end{minipage}
\end{center}

$x = -47 + 349n$ and $y = 40 + 297n$ are solutions to the equation.

\item Suppose you have two small champagne glasses, one holding 8 ounces and another holding 5 ounces. Is
it possible to fill one of the glasses with exactly 1 ounce of champagne? If so, how can this be done? If
not, prove that it cannot be done.
\begin{quote}
We need to find a solution to the Diophantine Equation
\[
8x+5y=1.
\]
We know that $gcd(8,5)=1$, and $1|1$, so there is a solution. Working backwards through the Euclidian
Algorithm gives us
\begin{align*}
1 &= 3-2(1)\\
&= 3(2)-5\\
&= 8(2)+5(-3).
\end{align*}
Therefore, if we fill the first glass up twice and empty the second glass three times, we will end up with
1 ounce leftover.
\end{quote}
\end{enumerate}
\end{document}
